Model

### 2019-09-04 stats/model.Rmd
record full distribution of predictions; change sopt to be a function of age rather than random intercept

      // question: should we use age here instead of the random intercept? or a different random intercept?
      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * subj_linguistic_competence

@@

@@

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 8,
  cores = 8,
  inference_opts = list(method = "incrementalMH",
                        samples = 4000,
                        burn = 2000,
                        verbose = T,
                        lag = 1,
                        verboseLag = 1000)
)

saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")

>>>>

     // display("age = " + subj_age + " ... intercept = " + subj_linguistic_competence)

      // question: should we use age here instead of the random intercept? or a different random intercept?
      var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * age

@@

  foreach(function(row){
      var prior = [row.prior, 1-row.prior]
      foreach(function(item){
        var itemLineParameters = all_item_parameters[item]
        var sem_knowledge = logistic(itemLineParameters.intercept + 
            itemLineParameters.slope * row.age)
        var speakerOptimality = speakerOptimalityParameters.intercept  + speakerOptimalityParameters.slope * row.age

        var modelPredictions = pragmaticListener({label: "novel_word"}, prior, speakerOptimality, sem_knowledge)
        query.add(["prediction", item, row.age], [row.alignment, Math.exp(modelPredictions.score(1))])

      }, familiars)
   }, dataFromR.comb_data)

@@

me_model_data <- read_csv("../data/me.csv")%>%
    filter(trial != "train1",
           trial != "train2")%>%
  mutate(age = age_num - min(age_num),
         nov_int = novel_params$Intercept,
         nov_slope = novel_params$age_num,
         prior = plogis(nov_int + age * nov_slope))

comb_model_data <- bind_rows(
  me_model_data %>%
    distinct(age, prior) %>%
    mutate(alignment = "congruent"),
  me_model_data %>%
    distinct(age, prior) %>%
    mutate(prior = 1 - prior, 
         alignment = "incongruent")
)

sem_know_model<- webppl(
  program_code = paste(rsaUtils, rsaModel, sem_subj_str , sep='\n'),
  data = list(data = me_model_data, comb_data = comb_model_data),
  data_var = "dataFromR",
  model_var = "model",
  chains = 1,
  cores = 1,
  inference_opts = list(method = "incrementalMH",
                        samples = 1,
                        burn = 1,
                        verbose = T,
                        lag = 1,
                        verboseLag = 10)
)

# saveRDS(sem_know_model, "../saves/sem_know_model_wide_sig_pos_slope_ind.rds")
